### 2018-04-26 contents/reviews/pain.tex
Updates from ShareLaTeX

\begin{figure}[ht]
\includegraphics[width=0.8\textwidth]{dorsal-lamina.pdf}
\centering
\caption{The axonal projections of the fast conduction ($ A\delta$) and slow conducting (C) pain stimuli in the dorsal horn.}
\label{fig:drg}
\end{figure}

@@

 \begin{figure}[ht]
 \includegraphics[width=\textwidth]{pain-pathways.jpg}
 \centering
 \caption{Afferent pain pathways \protect\cite{kandel2000principles}}
 \label{fig:pain-pathways}
 \end{figure}

@@

 \begin{figure}[ht]
 \includegraphics[width=0.8\textwidth]{pain-matrix.png}
 \centering
 \caption{ Cortical and sub-cortical regions of the pain matrix. \protect\cite{Tracey2007a}} 
 \label{fig:pain-matrix}
 \end{figure}

>>>>

\begin{figure}[ht]
\includegraphics[width=0.8\textwidth]{dorsal-lamina.pdf}
\centering
\caption{The axonal projections of the fast conduction ($ A\delta$) and slow conducting (C) pain stimuli in the dorsal horn. Modified from \protect\cite{DMello2008}}
\label{fig:drg}
\end{figure}

@@

 \begin{figure}[ht]
 \includegraphics[width=\textwidth]{pain-pathways.jpg}
 \centering
 \caption{Three of the five afferent pain pathways \protect\cite{kandel2000principles}. Reproduced with permission from Copyright Clearance Center (License ID: 4336310447247)}
 \label{fig:pain-pathways}
 \end{figure}

@@

 \begin{figure}[ht]
 \includegraphics[width=0.8\textwidth]{pain-matrix.png}
 \centering
 \caption{ Cortical and sub-cortical regions of the pain matrix \protect\cite{Tracey2007a}. Reproduced with permission from Copyright Clearance Center (License ID: 4316760598837).}
 \label{fig:pain-matrix}
 \end{figure}
